PCA on Finnish Municipalities

### 2022-04-08 MSA-Project.Rmd
Added table

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

@@

>>>>

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)

@@

## Variables and descriptive statistics

```{r}

vars <-  c('Prop.Urban.Areas', 'Pop', 'Pop.Change', 'Prop.Below15', 'Prop.15to64', 'Prop.Over64', 'Prop.Swedish', 'Prop.Foreign', 'Pop.Growth', 'Migr.Gain', 'Families', 'Households', 'Prop.Households.rowSmall', 'Prop.Households.Rent', 'Prop.Educ.Degree2', 'Prop.Educ.High', 'Employed', 'Empl.Rate', 'Prop.Households.Empl', 'Prop.Unempl', 'Prop.Pension', 'Support.Ratio', 'Jobs', 'Prop.Primary.Sector', 'Prop.Secondary.Sector', 'Prop.Services.Sector', 'Jobs.Self.Suff', 'Margin.Citizen', 'Loan.Citizen', 'Concern.Loan.Citizen', 'Educ.Cult.Citizen', 'Soc.Health.Citizen')
explanations <- rep("NA", length(vars))
var.df <- data.frame(vars, explanations)

knitr::kable(var.df, col.names = c("Variable", "Explanation"))
